### 2011-03-16 subarchitectures/vision.sa/branches/post-review-yr2-11533/src/c++/vision/components/VisualLearner/test/gy2report/gy2article.tex
report corrected

VisualObjects appear and disappear while the robot is processing tutor's
instructions. When a VisualObjects disappears from the WM, the planner usually
creates a plan that references an invalid belief. Such a plan remains in a {\tt
PENDING} state. The valid new plans that are created afterwards are in {\tt
SURFACED} state but are never {\tt ACTIVATED}.

@@

We have 1200 image pairs in the database. Some (less than 10) of the image
pairs cause the components {\em PlanePopout} or {\em SOIFilter} to crash. In
average we can run the system for about 100 objects before we have to restart
it.

We also made an interesting observation in the {\em stWaitForLearningTask}
state. This state is reached $2$ times while the object is on the scene. After
the tutor describes the shape, the first learning task is created after $3-5$
seconds. When the learning is complete the tutor then waits for $2s$ and
describes the color of the object.  The interesting thing about the second
LearningTask task is that it's time to appear increases with the system's
running time. Initially it is the same as for the first LearningTask. After
$4000s$ it increases to $7s$ and after $7000s$ it takes $12s$ for it to appear.
Finally the system stops resonding as described above.

>>>>

VisualObjects appear and disappear while the robot is processing tutor's
instructions. When a VisualObjects disappears from the WM, the planner usually
creates a plan that references an invalid belief. Such a plan remains in a {\tt
PENDING} state. The new goals that are created afterwards are in {\tt SURFACED}
state but are never {\tt ACTIVATED}. No new plans are created.

@@

We also made an interesting observation in the {\em stWaitForLearningTask}
state. This state is reached $2$ times while the object is on the scene. After
the tutor describes the shape, the first learning task is created after $3-5$
seconds. When the learning is complete the tutor then waits for $2s$ and
describes the color of the object.  The interesting thing about the second
LearningTask task is that it's time to appear increases with the system's
running time. Initially it is the same as for the first LearningTask. After
$4000s$ it increases to $7s$ and after $7000s$ it takes $12s$ for it to appear.
Finally the system stops resonding as described above.  The increasing time
could be related to the increasing number of messages from the planner:
``Pointer to belief xxx cannot be resolved''.

\subsection{Other crashes}

The c++ server sometimes crashes right after the message ``Planner has
attempted to overwrite an outdated WM entry. WMA:
XX:goal.scheduler:data:planner.sa.  Local version: 5.  WM version: 6''.

Some of the image pairs (less than 10 out of $1200$ in the database) cause the
components {\em PlanePopout} or {\em SOIFilter} to crash.

\subsection{Example log}

This is a part of the log file that shows the state transitions while the robot
is learning one object (approximately $50s$).

\begin{verbatim}
[INFO gy2article: 4218.43 NEW STATE stTableEmpty]
[INFO gy2article: 4220.43 SCENE 357: 1081vl]
[INFO gy2article: 4220.44 **********]
[INFO gy2article: 4220.44 NEW STATE stWaitToAppear (to=20s)]
[INFO gy2article: 4222.45 STATE stWaitToAppear]
[INFO gy2article: 4226.47 **********]
[INFO gy2article: 4226.47 NEW STATE stObjectOn]
[INFO analyzer: blockVisualObjectUpdates enable=true]
[INFO gy2article: 4231.47 **********]
[INFO gy2article: 4231.47 NEW STATE stTeaching (to=10s)]
[INFO SOI.filter: blockProtoObjectUpdates enable=true]
[INFO gy2article: 4232.47 Tutor: this is elongated]
[INFO gy2article: 4232.47 **********]
[INFO gy2article: 4232.47 NEW STATE stWaitForResponse (to=15s)]
[INFO gy2article: 4234.48 STATE stWaitForResponse]
[INFO gy2article: 4234.48 Robot says: thank you]
[INFO gy2article: 4234.48 **********]
[INFO gy2article: 4234.48 NEW STATE stWaitForLearningTask (to=120s)]
[INFO gy2article: 4237.06 Learnig task added: [WMA: vision.sa:o2:J]]
[INFO gy2article: 4240.21 Learnig task changed: [WMA: vision.sa:o2:J]]
[INFO gy2article: 4240.21 A Learning Task was detected.]
[INFO gy2article: 4240.21 **********]
[INFO gy2article: 4240.21 NEW STATE stTeaching (to=10s)]
[INFO gy2article: 4241.22 Tutor: this is black]
[INFO gy2article: 4241.22 **********]
[INFO gy2article: 4241.22 NEW STATE stWaitForResponse (to=15s)]
[INFO gy2article: 4243.23 Robot says: thank you]
[INFO gy2article: 4243.23 **********]
[INFO gy2article: 4243.23 NEW STATE stWaitForLearningTask (to=120s)]
[INFO gy2article: 4249.55 Learnig task added: [WMA: vision.sa:p2:J]]
[INFO gy2article: 4256.04 Learnig task changed: [WMA: vision.sa:p2:J]]
[INFO gy2article: 4256.05 A Learning Task was detected.]
[INFO gy2article: 4256.05 **********]
[INFO gy2article: 4256.05 NEW STATE stTeaching (to=10s)]
[INFO gy2article: 4257.06 **********]
[INFO gy2article: 4257.06 NEW STATE stEndOfTeaching (to=15s)]
[INFO gy2article: 4257.08 **********]
[INFO gy2article: 4257.08 NEW STATE stUnloadScene]
[INFO analyzer: blockVisualObjectUpdates enable=false]
[INFO gy2article: 4262.10 SCENE: empty]
[INFO SOI.filter: blockProtoObjectUpdates enable=false]
[INFO gy2article: 4262.10 **********]
[INFO gy2article: 4262.10 NEW STATE stWaitToDisappear (to=20s)]
[INFO gy2article: 4264.11 STATE stWaitToDisappear]
[INFO gy2article: 4268.13 **********]
[INFO gy2article: 4268.13 NEW STATE stTableEmpty]
\end{verbatim}
